---
title: 'Deep Visual Inference: Teaching Computers To See Rather Than Calculate Correlation'
author: "Giora Simchoni"
output: html_notebook
subtitle: BGU IE&M Dept. Seminar 2019
datae: December 9th, 2019
---

```{r Libs}
library(tidyverse)
library(ggmosaic)
library(knitr)
library(glue)
library(ggbeeswarm)
library(scales)
library(nullabor)
```
# Prologue (with OkCupid)

## Ever wondered...

Is there a relation between age and height (say, for adult women)?

```{r Prologue1}
okcupid <- read_csv("data/okcupid.csv")

okcupid_fil <- okcupid %>%
  filter(sex == "f", age < 80, between(height, 120, 220))

theme_update(text = element_text(size=18))

okcupid_fil %>%
  count(age, height) %>%
  ggplot(aes(age, height)) +
  geom_point(aes(size = n), color = "blue")
```

```{r Prologue1-Stat}
cor.test(okcupid_fil$age, okcupid_fil$height)
```

Is there a relation between ethnicity and (reported) drug abuse?

```{r Prologue2}
okcupid <- okcupid %>%
  mutate(drugs = forcats::fct_relevel(drugs, c("never", "sometimes", "often")),
         ethnicity = forcats::fct_relevel(ethnicity, c("white", "black", "latin", "asian", "other")))
ggplot(okcupid) +
  geom_mosaic(aes(x = product(drugs, ethnicity), fill=drugs), na.rm = TRUE) +
  labs(x = "", y = "") +
  guides(fill=FALSE) +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5))
```

```{r Prologue2-Table}
library(knitr)
prop.table(table(okcupid$ethnicity, okcupid$drugs), 1) %>%
  kable(digits = 2)
```

```{r Prologue2-Stat}
chisq.test(table(okcupid$ethnicity, okcupid$drugs))

# Define Cramer's V function (or get it from various packages)
cramer_v <- function(x) {
  unname(sqrt(chisq.test(x)$statistic /(sum(x) * (min(nrow(x),ncol(x)) - 1))))
}

cv <- cramer_v(table(okcupid$ethnicity, okcupid$drugs))
glue("Cramer's V: {format(cv, digits = 2)}")
```

Is there a relation between sexual orientation and height?

```{r Prologue3}
okcupid_fil <- okcupid %>%
  filter(orientation %in% c("straight", "gay"), between(height, 120, 220))

sex_names <- list(
  "m" = "men",
  "f" = "women"
)

sex_labeller <- function(variable, value){
  return(sex_names[value])
}

okcupid_fil %>%
  sample_n(5000) %>%
  ggplot(aes(orientation, height, color = orientation)) +
  geom_quasirandom() +
  facet_wrap(~ sex, labeller = sex_labeller) +
  guides(color = FALSE)
```

```{r Prologue3-Table}
okcupid_fil %>%
  group_by(sex, orientation) %>%
  summarise(mean = mean(height), std = sd(height), n = n()) %>%
  kable(digits = 1)
```

```{r Prologue3-Stat}
okcupid_fil_m <- okcupid_fil %>% filter(sex == "m")
okcupid_fil_f <- okcupid_fil %>% filter(sex == "f")

t.test(height ~ orientation, data = okcupid_fil_m)
t.test(height ~ orientation, data = okcupid_fil_f)
```

```{r Prologue4}
okcupid_fil <- okcupid %>%
  filter(income > 0, between(height, 120, 220))

okcupid_fil %>%
  count(income, height, sex) %>%
  ggplot(aes(height, income)) +
  geom_point(aes(size = n), color = "blue") +
  facet_wrap(~ sex, labeller = sex_labeller) +
  scale_y_log10(breaks = trans_breaks("log10", function(x) 10^x),
              labels = trans_format("log10", math_format(10^.x)))
```
# Line 'Em Up!

Is there a relation between a car's Engine Displacement and its Horse Power? (n = 32)

```{r Lineup-example1}
# reading from disk for reproducibility, however you should use the nullabor lineup function

# lineup_data_mtcars <- lineup(null_permute("hp"), mtcars)
# saveRDS(lineup_data_mtcars, "data/lineup_data_mtcars.RData")
lineup_data_mtcars <- readRDS("data/lineup_data_mtcars.RData")

theme_update(text = element_text(size=14))

ggplot(lineup_data_mtcars, aes(disp, hp)) +
  geom_point(color = "blue") +
  facet_wrap(~ .sample) +
  labs(title = "Is there a relation between a car's Engine Disp. and HP? (n = 32)")
```

```{r Lineup-example1-True}
attr(lineup_data_mtcars, "pos")
```
Is there a relation between Gender and Answer? (n = 843)

Q: Is it rude to bring a baby on plane?

```{r Lineup-example2}
fly2 <- fly %>%
  mutate(
    RudeToBringBaby = forcats::fct_recode(RudeToBringBaby, No = "No, not at all rude", Somewhat = "Yes, somewhat rude", Yes = "Yes, very rude"),
    RudeToRecline = forcats::fct_recode(RudeToRecline, No = "No, not rude at all", Somewhat = "Yes, somewhat rude", Yes = "Yes, very rude"),
    RudeToBringBaby = forcats::fct_relevel(RudeToBringBaby, c("Yes", "Somewhat", "No")),
    RudeToRecline = forcats::fct_relevel(RudeToRecline, c("Yes", "Somewhat", "No")))

# reading from disk for reproducibility, however you should use the nullabor lineup function

# lineup_data_fly <- lineup(null_permute("Gender"), fly2)
# saveRDS(lineup_data_fly, "data/lineup_data_fly.RData")
lineup_data_fly <- readRDS("data/lineup_data_fly.RData")

theme_update(text = element_text(size=12))

ggplot(lineup_data_fly) +
  geom_mosaic(aes(x = product(RudeToBringBaby, Gender), fill=RudeToBringBaby), na.rm=TRUE) +
  labs(x = "", y = "") +
  scale_fill_ordinal(name = "") +
  facet_wrap(~ .sample) +
  labs(title = "Is there a relation between Gender and Answer? (n = 843)",
       subtitle = "Q: Is it rude to bring a baby on plane?")
```

```{r Lineup-example2-True}
attr(lineup_data_fly, "pos")
```

Is there a relation between an actor's gender and no. of roles since his/her character ended? (n = 129)

```{r Lineup-example3}
roles_after_char_end <- read_csv("data/roles_after_char_end.csv") %>%
  select(Gender, n_roles) %>%
  drop_na()

# reading from disk for reproducibility, however you should use the nullabor lineup function

# lineup_data_roles <- lineup(null_permute("Gender"), roles_after_char_end)
# saveRDS(lineup_data_roles, "data/lineup_data_roles.RData")
lineup_data_roles <- readRDS("data/lineup_data_roles.RData")

wrapper <- function(x, ...) 
{
  paste(strwrap(x, ...), collapse = "\n")
}

ggplot(lineup_data_roles, aes(Gender, n_roles, col = Gender)) +
  geom_beeswarm() +
  labs(x = "", y = "",
       caption = "Emmy nominated US drama shows 2000-2014, appeared in at least half the episodes, 4+ years since character end") +
  guides(color=FALSE) +
  facet_wrap(~ .sample) +
  labs(title = wrapper("Is there a relation between an actor's gender and no. of roles since his/her character ended? (n = 129)", width = 80))
```

```{r Lineup-example3-True}
attr(lineup_data_roles, "pos")
```

# Wait, did you just say "judge a plot", as in "classify an image", and the year is >= 2012?

For full code of neural network, including the results and "where things become interesting / wrong" parts, the scatterplot case - see my blog post [Book'em Danno!](http://giorasimchoni.com/2018/02/07/2018-02-07-book-em-danno/) and this [dl_pearson_r_additional_code_to_blog.R]() file in repo

For full code of neural network, the mosaic case - see this [dl_cramer_v.R]() script in repo.

```{r SessionInfo}
sessionInfo()
```